---
title: "Netlify"
format: revealjs
editor: visual
---

+ https://jadeyryan.com/blog/2023-11-19_publish-quarto-website/
+ https://github.com/JohnGavin/quarto_website
  + _not_ https://github.com/JohnGavin/quarto_blog

+ GitHub account in RStudio
  + connect
  + authenticated 

## use_git create repo
```{r use_git create repository}
#| eval = FALSE
if (!require(pacman)) install.packages('pacman')
pacman::p_load(usethis)
usethis::use_git()
```

## use_github connect repo

```{r use_github connect repo}
#| eval = FALSE
usethis::use_github()
```

## Quarto CLI publish 
+ From terminal window
  + _not_ from a bash chunk
```{bash Quarto CLI publish}
#| eval = FALSE
quarto publish netlify
```

+ run `quarto render` 
  + in the terminal 
  + updates _freeze directory
+ always `quarto render` 
  + before Github pushing

## continuous deployment
+ https://jadeyryan.com/blog/2023-11-19_publish-quarto-website/#configure-netlify-plugin
+ freeze computations so code only runs locally
  + results in html.json file in _freeze folder

## push a change
+ https://jadeyryan.com/blog/2023-11-19_publish-quarto-website/#push-a-change-to-our-repo
